\documentclass{socyti}
\addbibresource{references.bib} %Imports bibliography file

% Document Variables
\title{Violence-Inducing Behaviour Prevention in Social-Cyber Space of Local Communities}
\author[1]{Author Authorson}
\author[2]{Author Author}
\affil[1]{Organisation}
\affil[2]{Organisation}
\date{\today}
\deliverable{X.Y}
\subtitle{Title}
\annotation{ANNOTATION}
\wpnumber{NUMBER}
\wptitle{WP Title}
\shorttitle{Short Title}
\distlevel{Public (P)}
\duedate{\formatdate{01}{08}{2022}}
\relateddeliverables{DX.Y, DX.Y}
\leadingpartners{Organisation}

% Document
\begin{document}
    \maketitle

    % History
    \textbf{History}\footnote{History will be deleted before final submission.}
    NB: a \textbf{status} is associated to each step of the document lifecycle:
    \begin{itemize}
        \item \textbf{Draft}: this version is under development by one or several partner(s).
        \item \textbf{Under Review}: this version has been sent for internal review.
        \item \textbf{Issued}: this version of the document has been submitted.
    \end{itemize}

    \begin{table}[h]
        \begin{tabularx}{\textwidth}{|X|X|X|X|X|}
            \hline
            \rowcolor{rowgray}
            Version & Status & Date & Author & Main Changes \\
            \hline
        \end{tabularx}
    \end{table}

    \textbf{Disclaimer:}

    \textbf{This report is part of the SOCYTI project which has received funding by the Research Council of Norway as a Researcher Project for Technological Convergence related to Enabling Technologies. The content of this report reflects only the authors’ view. The Research Council of Norway is not responsible for any use that may be made of the information it contains.}

    \newpage

    % Executive Summary
    {\Large\textbf{Executive Summary}}

    Include an executive summary with a combination of the abstract and the main conclusions.

    \newpage

    \tableofcontents

    \newpage

    \listoffigures

    \newpage
    
    \listoftables

    \newpage

    % Glossary

    {\Large\textbf{Glossary}}

    Please add a brief explanation of all used abbreviations and specific expression used in this document (in alphabetical order). Consider the background and knowledge of the target audience described before.

    \begin{table}[h]
        \begin{tabularx}{\textwidth}{|l|X|}
            \hline
            \rowcolor{rowgray}
            Abbreviation & Expression \\
            \hline
            SOCYTI & Violence-Inducing Behaviour Prevention in Social-Cyber Space of Local Communities \\
            \hline
        \end{tabularx}
    \end{table}

    \newpage

    \pagenumbering{arabic}

    \setcounter{page}{1}

    \input{sections/first-section.tex} \newpage
    \input{sections/second-section.tex} \newpage

    \printbibliography

    \pagenumbering{gobble}
\end{document}